### 2020-04-21 final_report/results.tex
add two paragraphs about hyperparameter tuning results

>>>>

The first two experiments perform Bayesian optimisation to maximise~$R^2$ in
cross-validated setting as a function of model hyperparameters. While in the
first experiment we limit ourselves to the scope of a single slice of the
domain, in the second experiment we extend the process to the full feature
space.

The results displayed in~\cref{fig:time-vs-reg} indicate that in the first
experiment, gradient boosted trees clearly appear to be the most accurate as
well as the fastest surrogate class in terms of mean prediction time. Following
that, we note that extremely randomised trees, support vector machines and
neural networks also achieved satisfactory results in both examined metrics.
While the remainder of tested surrogate classes does not exhibit problems in
complexity, its regression performance falls below average.

% TODO: multislice description
